Analytical choices for analyzing multidimensional behavior - many analyst test hypotheses about human speech.

### 2020-12-02 RR_manuscript/Draft_RR.Rmd
merged meta analysis write up

They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g. Box 1976, Tukey 1977, de Groot 2014). 
They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al. 2011). <!-- taken for granted? --> 
Recent projects have shown that the variability between different data analysts is vast.
This variability can lead independent researchers to draw vastly different conclusions about the same dataset (e.g. Silberzahn et al. 2018, Starns et al. 2019, Botvinik-Nezer et al., 2020). 
These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of datasets. 
Human behavior is complex and offers many ways to be translated into numbers. 
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data. 
In fields working on human speech production, for example, researchers need to make numerous decisions about what how to measure it. 
This is not trivial given the temporal extension of the acoustic signal and its complex structural composition. 
Not only can decisions about measuring the signal influence downstream decisions about statistical modelling, but statistical results can also lead researchers to go back and revise earlier decisions about the measuring process.

In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data. 
We explore the interaction between analytic choices at the stage of the operationalization of raw data and subsequent statistical modelling. 
Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams that gained access to the same set of acoustic recordings to answer the same research question.

@@

Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply. 
However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes. 
This can be problematic because to err is human. <!-- I'd probably drop this. When we make unspecified decisions during data analysis we can stumble upon spurious results (most likely) as well as real results (less likely, still possible)... in other words it might not all be error... the issue is that we won't know the difference -->

We have evolved to filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing ourselves of the validity of prior expectations (“I knew it”, Nickerson 1998), and perceiving events as being plausible in hindsight (“I knew it all along”, Fischhoff 1975). <!-- JC: If helpful we could also give a concrete common example here, like regarding forecasting the weather or something --> 
<!-- TR: Generally a good idea, but I'd say we keep it crisp at that point. The take-home here is: Humans are biased. --> 
In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole & Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few. 
This issue is particularly amplified in fields in which the raw data lend themselves to flexible measurement (Roettger 2019). 
Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions

Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g. Simmons et al. 2011, Gelman & Loken 2013). 
These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record. 
Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical reanalyses of published analytic strategies are uncommon because data sharing is still rare (Wicherts, Borsboom, Kats, & Molenaar, 2006, RECENT REF).

@@

While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modelling. 
In these studies the datasets were fixed and data collection or measurement could not be changed. <!-- JC: any particular reason to favor data table over dataset? --> <!-- TR: I think my reasoning was dataset can be data table or raw data. Data table is the numerical derivation of the raw data. Maybe not a useful distinction-->

However, in many fields the primary raw data are complex signals that need to be operationalized according to the research question. 
In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual and/or acoustic signal.
Decisions about how to measure a theoretically construct of that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse. 
To understand how analytical flexibility manifests itself in a scenario where a complex decisions procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set

@@

In order to understand speech, listeners have to map a continuous, transient signal onto discrete meanings. Take for example the sentence: "The president refused to concede". This sentence stretches over hundreds of milliseconds and contains several layers of linguistically relevant units such as words, syllables and individual sounds. Thus, it offers a considerable number of perspectives and decisions along the data analysis pipeline. 
When conducting a study on speech production, the first important analytic decision to test a hypothesis relates to operationalization of the relevant behavior, i.e. how to measure the phenomenon of interest. 
For example, how do we measure whether two sounds are acoustically identical or not (e.g. "concede" vs. "conceal"), whether one word is more prominent than others ("The president REFUSES to concede"), or whether two discourse functions are produced differently ("The president refuses to concede." vs. "The president refuses to concede?")? 
In other words, how do we quantitatively capture relevant features of speech that correspond to the target behavior?
This is not trivial. 
Speech categories are inherently multidimensional and vary through time. 
The acoustic parameters for one category are usually asynchronous, i.e. appear at different points of time in the unfolding signal and overlap with parameters for other categories (e.g. Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014). 
For example, the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in "bear" vs. "pear") can be manifested by many different acoustic measures (Lisker, 1977). 
Even temporally dislocated acoustic parameters correlate with this lexical contrast. 
For example, in the English words "led" versus "let", voicing correlates can be found in the acoustic manifestation of the initial /l/ of the word (Hawkins & Nguyen, 2004).
The apparent multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech. 
Studies investigating acoustic correlates of word stress (e.g. the difference between "insight" and "incite"), for example, have been using many different measurements, including temporal characteristics (duration of certain segments or subphonemic intervals), spectral characteristics (intensity measures, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g. Gordon & Roettger, 2017). 
Looking at even larger domains, the expression of pragmatic functions can be expressed by a variety of structurally different acoustic cues which can be distributed throughout the entire utterance. 
Discourse functions are systematically expressed by multiple local pitch modulations differing in their position, shape, and alignment (e.g. Niebuhr et al., 2011). 
They can also be expressed by global or local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005). 
All of these phonetic parameters are potential manifestations of underlying functional contrasts, like speaker's intentions, levels of arousal or social identity. 
When testing hypotheses on speech production data, researchers need to make many decisions. 
The larger the functional domain (e.g. are we interested in lexical items or in whole utterances), the higher the number of possible operationalizations. 
These decisions are usually made prior to any statistical analysis, but can possibly be revised a posteriori in light of downstream analytic decisions. 
To probe the variability in data analysis pipelines across independent analytic teams, we provided researchers with an experimentally elicited speech corpus that looked at a functional contrast that is potentially manifested across the whole utterance.

@@

## Research questions

# Methods (mostly copy-paste from Evo-RR)

We are closely following the methodology proposed by Parker et al. (Stage 1 in-principle accepted).

This project involves a series of steps (X-X) that begins with recruiting independent groups of scientists to analyze the data, continuing through allowing the scientists to analyze the data as they see fit, generating peer review ratings of the analyses (based on methods, not results), evaluating the variation among the different analyses, and producing the final manuscript. 
We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report, will take XX months (Table X). 
The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent groups of scientists.

## Step 1: Recruitment and Initial Survey of Analysts

Initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accesibilty to potential analysts (LINK). 
The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth. 
The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline. 
Researchers can choose to work independently or in a small team. 
For the sake of simplicity, we refer to single researcher or small teams as ‘analysis teams’.

@@

<!-- TR: So I am still unclear on how this will look like, do they only evaluate stats? if they evaluate the entire pipeline they need to be phoneticians, do they evaluate acoustic analysis and stats analysis independently?-->

At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited). 
Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts. 
Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors (SC, JC, TR). 
The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer. 
For instance, if each reviewer is assigned four analyses to review, then each analysis will be the first analysis assigned to at least one reviewer, the second analysis assigned to another reviewer, the third analysis assigned to yet another reviewer, and the fourth analysis assigned to a fourth reviewer. 
Balancing the order in which reviewers see the analyses controls for order effects, e.g. a reviewer might be less critical of the first methods section they read than the last.
The process for a single reviewer will be as follows. 
First, the reviewer will receive a description of the methods of a single analysis. 
This will include the narrative methods section, the analysis team’s answers to our survey questions regarding their methods, including analysis code, and the data set. 
The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on these prompts: <!-- TR:Need flow chart here-->

@@

- 100. A perfect analysis with no conceivable improvements from the reviewer
- 75. An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation
- 50. A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty
- 25. A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty
- 0. A dangerously misleading analysis, certain to produce both an estimate that is wrong and a substantially over-precise estimate of uncertainty that places undue confidence in the incorrect estimate.

@@

## Step 4: Evaluate Variation
Initiating authors (SC, JC, TR) will conduct the analyses outlined in this section. 
We will describe the variation in model specification in several ways:
First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures, the operationalization and the temporal domain of measurement, the nature and number of model parameters for both fixed and random effects [if applicable], as well as the mean, standard deviation and range of effect sizes reported.

@@

@@

Effect size ($\delta_{t}$) is the outcome variable and the number of post-hoc changes and the number of models fit will be included as population-level effects (i.e., fixed effects). 
The likelihood of the outcome variable is assumed to be normally distributed.
Analysis teams and reviewers will be included as group-level effects (i.e., random effects). 
For all population-level parameters, the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1. 
A cauchy prior set at 0 with scale 1 will be used for $\tau$. 
We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
The analysis will be conducted in R (R core team, 2020) and fit using `stan` (Stan, 2019) via the R package `brms` (Bürkner, 2019).

<!-- Sorensen analysis starts here -->

The pooled estimate of the meta-analytic model will be used in a series of descriptive analyses that serve the purpose of describing how individual teams vary from each other. 
Specifically, we will explain how team effect sizes deviate from the pooled estimate based on a measure of the uniqueness of the set of variables included in each analysis. 
We will use Sorensen's Similarity Index (SSI) to derive a 'uniqueness' score. 
The SSI is an index typically used in ecology research to compare species composition across sites. 
For our purposes, we will treat variables as species and individual analyses as sites.
In order to generate an SSI for each analysis team, we will calculate the average of all pairwise Sorensen's values for all pairs of analyses using the betapart package (Baselga et al. 2018) in R. 
We achieve this using the following formula:

@@

where, given a pair of models, a is the number of variables common to both, b is the number of variables that occur in the first model but not in the second, and c is the number of variables that occur in the second model but not in the first. 
We then will use the per-model average Sorensen's index value as an independent variable to predict the deviation score in a general linear model, with no random effect since each analysis is included only once, in the stats package in R  (R_Core_Team 2019):
<!-- are we going to do this last part? -->

WRITE ABOUT HOW TO HANDLE GAMS

@@

ADD GAM EXCLUSION

DESCRIBE META-NALYSIS

We will assess the extent to which deviations from the meta-analytic mean by individual effect sizes can be explained by the following predictors:

The peer ratings (1-100) of each analysis, a measurement of the ‘uniqueness’ of the set of model parameters included in each analysis (see below), whether or not analysis teams have changed their analyses in a post hoc fashion (EXPLAIN ABOVE, binary), the number of analyses performed before the final model was performed (as self-estimated by the teams).

The uniqueness of model parameters will be assessed using the Sorensen’s Similarity Index (an index typically used to compare species composition across sites). Here we treat model parameters as species and individual analyses as sites. To generate an individual Sorensen’s value for each analysis requires calculating the pairwise Sorensen’s value for all pairs of analyses (of the same data set), and then taking the average across these Sorensen’s values for each analysis. We will calculate the Sorensen’s index values using the betapart package (Baselga et al. 2018) in R:

$$\beta_{Sorensen} = \frac{b+c}{2_a + b + c}$$

The individual posterior mean for each analysis of each team serves as the dependent variable in these analyses.

>>>>

They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g. Box 1976, Tukey 1977, de Groot 2014). 
They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al. 2011). <!-- taken for granted? --> 
Recent projects have shown that the variability between different data analysts is vast.
This variability can lead independent researchers to draw vastly different conclusions about the same dataset (e.g. Silberzahn et al. 2018, Starns et al. 2019, Botvinik-Nezer et al., 2020). 
These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of datasets. 
Human behavior is complex and offers many ways to be translated into numbers. 
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data. 
In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it. 
This is not trivial given the temporal extension of the acoustic signal and its complex structural composition. 
Not only can decisions about measuring the signal influence downstream decisions about statistical modelling, but statistical results or modelling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.

In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data, a process that involves both decisions regarding the operationalization of a complex observed signal and decisions regarding the statistical modelling.
Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams who gained access to the same set of acoustic recordings in order to answer the same research question.

@@

Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude in the final analysis, what models to use or what inferential decision procedure to apply. 
However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes. 
This can be problematic because to err is human. <!-- I'd probably drop this. When we make unspecified decisions during data analysis we can stumble upon spurious results (most likely) as well as real results (less likely, still possible)... in other words it might not all be error... the issue is that we won't know the difference -->
<!-- TR: But isn't the human bias the major issue in statistical misinterpretation? (It also leads naturally to the next paragraph.) -->

We have evolved to filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing ourselves of the validity of prior expectations (“I knew it”, Nickerson 1998), and perceiving events as being plausible in hindsight (“I knew it all along”, Fischhoff 1975). <!-- JC: If helpful we could also give a concrete common example here, like regarding forecasting the weather or something --> 
<!-- TR: Generally a good idea, but I'd say we keep it crisp at that point. The take-home here is: Humans are biased. --> 
In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole & Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few. 
This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger 2019). 
Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions
Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g. Simmons et al. 2011, Gelman & Loken 2013). 
These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record. 
Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical reanalyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, & Molenaar, 2006, RECENT REF).

@@

While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modelling. 
In these studies the datasets were fixed and data collection or measurement could not be changed. <!-- JC: any particular reason to favor data table over dataset? --> <!-- TR: I think my reasoning was dataset can be data table or raw data. Data table is the numerical derivation of the raw data. Maybe not a useful distinction?-->

However, in many fields the primary raw data are complex signals that need to be operationalized according to the research question. 
In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
Decisions about how to measure a theoretically construct related to that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse. 
<!-- TR:maybe give a concrete example, how such an interactionn would look like for speech data?-->

To understand how analytical flexibility manifests itself in a scenario where a complex decisions procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set

@@

In order to understand speech, listeners have to map a continuous, transient signal onto discrete meanings. Take for example the sentence: "The president refused to concede". This sentence stretches over hundreds of milliseconds and contains several layers of linguistically relevant units such as words, syllables and individual sounds. Thus, it offers a considerable number of perspectives and decisions along the data analysis pipeline. 
When conducting a study on speech production, the first important analytic decision to test a hypothesis relates to operationalization of the relevant behavior, i.e. how to measure the phenomenon of interest. 
For example, how do we measure whether two sounds are acoustically identical or not (e.g. "concede" vs. "conceal"), whether one word is more prominent than others ("The president REFUSES to concede"), or whether two discourse functions are produced differently ("The president refuses to concede." vs. "The president refuses to concede?")? 
In other words, how do we quantitatively capture relevant features of speech that correspond to the target behavior?
This is not trivial. 
Speech categories are inherently multidimensional and vary through time. 
The acoustic parameters for one category are usually asynchronous, i.e. appear at different points of time in the unfolding signal and overlap with parameters for other categories (e.g. Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014). 
For example, the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in "bear" vs. "pear") can be manifested by many different acoustic measures (Lisker, 1977). 
Even temporally dislocated acoustic parameters correlate with this lexical contrast. 
For example, in the English words "led" versus "let", voicing correlates can be found in the acoustic manifestation of the initial /l/ of the word (Hawkins & Nguyen, 2004).
The apparent multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech. 
Studies investigating acoustic correlates of word stress (e.g. the difference between "insight" and "incite"), for example, have been using many different measurements, including temporal characteristics (duration of certain segments or subphonemic intervals), spectral characteristics (intensity measures, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g. Gordon & Roettger, 2017). 
Looking at even larger domains, the expression of pragmatic functions can be expressed by a variety of structurally different acoustic cues which can be distributed throughout the entire utterance. 
Discourse functions are systematically expressed by multiple local pitch modulations differing in their position, shape, and alignment (e.g. Niebuhr et al., 2011). 
They can also be expressed by global or local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005). 
All of these phonetic parameters are potential manifestations of underlying functional contrasts, like speaker's intentions, levels of arousal or social identity. 
When testing hypotheses on speech production data, researchers need to make many decisions. 
The larger the functional domain (e.g. are we interested in lexical items or in whole utterances), the higher the number of possible operationalizations. 
These decisions are usually made prior to any statistical analysis, but can possibly be revised a posteriori in light of downstream analytic decisions. 
To probe the variability in data analysis pipelines across independent analytic teams, we provided researchers with an experimentally elicited speech corpus that looked at a functional construct that might be manifested across the whole utterance.

@@

## Research questions
The present project examines the extent to which subjective choices by different researchers analyzing a complex speech data set affect the reported results. We are further interested in which factors  affect researchers' final results.

# Methods (mostly copy-paste from Evo-RR)
We are closely following the methodology proposed by Parker et al. (Stage 1 in-principle accepted).

This project involves a series of steps (X-X): 
First, we recruite independent groups of researchers to analyze the data.
Second, We give researchers access to the speech corpus and let them analyze the data as they see fit. 
Third, we generate peer review ratings of the analyses (based on methods, not results).
Forth, we evaluate the variation among the different analyses.
And finally, we collaboratively produce the final manuscript. 
We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report, will take XX months (Table X). 
The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent groups of scientists.

## Step 1: Recruitment and Initial Survey of Analysts
Initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accesibilty to potential analysts (LINK). 
The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth. 
The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline. 
Researchers can choose to work independently or in a small team. 
For the sake of simplicity, we refer to single researcher or small teams as ‘analysis teams’.

@@

<!-- TR: So I am still unclear on how this will look like, do they only evaluate stats? if they evaluate the entire pipeline they need to be phoneticians, do they evaluate acoustic analysis and stats analysis independently?-->
At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited). 
<!-- TR: I have a hunch that finding reviewers will potentially be more difficult than finding analysis teams. They had as many reviewers as they had teams.-->
Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts. 
Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors. 
The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer. 
For instance, if each reviewer is assigned four analyses to review, then each analysis will be the first analysis assigned to at least one reviewer, the second analysis assigned to another reviewer, the third analysis assigned to yet another reviewer, and the fourth analysis assigned to a fourth reviewer. 
Balancing the order in which reviewers see the analyses controls for order effects, e.g. a reviewer might be less critical of the first methods section they read than the last.
The process for a single reviewer will be as follows. 
First, the reviewer will receive a description of the methods of a single analysis. 
This will include the narrative methods section, the analysis team’s answers to our survey questions regarding their methods, including analysis code, and the data set. 
The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on these prompts: <!-- TR:Need flow chart here-->

@@

- 100. A perfect analysis with no conceivable improvements from the reviewer.
- 75. An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation
- 50. A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty
- 25. A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty
- 0. A dangerously misleading analysis, certain to produce both an estimate that is wrong and a substantially over-precise estimate of uncertainty that places undue confidence in the incorrect estimate.

@@

## Step 4: Evaluate Variation
Th initiating authors (SC, JC, TR) will conduct the analyses outlined in this section. 
We will describe the variation in model specification in several ways:
First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures, the operationalization and the temporal domain of measurement, the nature and number of model parameters for both fixed and random effects [if applicable], the nature an reasoning behind inferential assessments, as well as the mean, standard deviation and range of effect sizes reported.

@@

<!-- TR: Do we still need standardized effect sizes? to compare shit or are we just going to compare their estimates? -->

@@

Effect size ($\delta_{t}$) will be the outcome variable.
The likelihood of the outcome variable is assumed to be normally distributed.
Analysis teams and reviewers will be included as group-level effects (i.e., random effects). 
For all population-level parameters, the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1. 
A cauchy prior set at 0 with scale 1 will be used for $\tau$. 
We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
The analysis will be conducted in R (R core team, 2020) and fit using `stan` (Stan, 2019) via the R package `brms` (Bürkner, 2019).

We will assess the extent to which the meta-analytic estimate is modulated by the following predictors:
The peer ratings of each analysis (numeric, 1-100), a measurement of the ‘uniqueness’ of the set of model parameters included in each analysis (see below, numeric), whether or not analysis teams have changed their analyses in a post hoc fashion (EXPLAIN ABOVE, binary), the number of analyses performed before the final model was performed (as self-estimated by the teamsm, numeric).
The measure of the uniqueness of the set of model parameters is assessed by the Sorensen's Similarity Index (SSI). The SSI is an index typically used in ecology research to compare species composition across sites. 
For our purposes, we will treat variables as species and individual analyses as sites.
In order to generate an SSI for each analysis team, we will calculate the average of all pairwise Sorensen's values for all pairs of analyses using the betapart package (Baselga et al. 2018) in R. 
We achieve this using the following formula:

<!--TR: question: do we just want to look if the meta analytical estimate is modulated by our preidctors or do we want to look at the individuals teams deviations from the meta estimate are modulated by our predictors?-->

<!--old :The pooled estimate of the meta-analytic model will be used in a series of descriptive analyses that serve the purpose of describing how individual teams vary from each other.-->

@@

WRITE ABOUT HOW TO HANDLE GAMS
<!--TR: maybe don't mention? -->

@@
